---
title: "Home"
---

This is the homepage of a Quarto website.

To learn more about Quarto websites visit <https://quarto.org/docs/websites>.

## This is a level 2 heading

This is text. Below is some R code. 

```{r}
1 + 1
```

## Run the analysis

We can run our analysis right in this document.

```{r}
#| warning: false

library(tidyverse)

data <- read_csv("data/ideology_foodstamps.csv")
```
We just loaded some data we created last week. Now we can do something with it. 

```{r}
glimpse(data)
```

## How do I use R, Quarto, and Github pages to publish a site?

Quarto will turn your R content into HTML, which you can in turn publish with Github Pages.

```{mermaid}
flowchart TD
    A[Start: Develop content in R] -->|Create and analyze data| B[Use Quarto to convert R Markdown to HTML]
    B --> C{Check if ready to publish}
    C -->|Yes| D[Push content to GitHub repository]
    C -->|No| A
    D --> E[Configure GitHub Pages in the repository settings]
    E --> F[Publish website via GitHub Pages]
    F --> G[Website Live]

```

## How do I use Quarto for reproducible research?

Just like making a website, except this time we start by conducting the research. 

```{mermaid}
flowchart TD
    A[Start: Research Question] -->|Data Collection| B[Data Analysis in R]
    B -->|Document with R Markdown| C[Reproducible Analysis in R]
    C --> D[Convert R Markdown to HTML using Quarto]
    D --> E{Check for Reproducibility and Accuracy}
    E -->|Yes| F[Version Control with GitHub]
    E -->|Revise| C
    F -->|Push to Repository| G[Configure GitHub Pages for Publishing]
    G --> H[Publish Reproducible Research Website via GitHub Pages]
    H --> I[Website Live: Share Research]
```
